### 2019-09-25 revised_dmtcs.d/symmetry_properties.tex
ssr: minor changes

When an $r$-symmetric function $f$ with $n$ variables is
specified using the table representation described in the
statement of Theorem~\ref{thm:rsym_canalyzing},
the size of the table is $O(n^r)$.
When $r$ is \emph{fixed}, the size of 
this representation and the running time 
of the above algorithm are both polynomial functions of $n$.

>>>>

When an $r$-symmetric function $f$ with $n$ variables is
specified using the table representation described in the
statement of Theorem~\ref{thm:rsym_canalyzing},
the size of the table is $O(n^r)$.
When $r$ is \emph{fixed}, the size of 
this representation and the running time 
of the above algorithm are both polynomials functions of $n$. 
However, when $r$ is a function of $n$, the size
of the input and the running time of the algorithm are
not polynomial functions of $n$.
